{\bf Topology, Geometry and Morphology of the Dark Matter Web}

### 2018-07-24 Draft/Chapter6/concl.tex
final changes

\begin{itemize}
% \subsection{Hierarchical structure of the dark matter web}
\item {\bf Hierarchical structure of the dark matter web: } The first study of the multi-stream environment of dark matter haloes in cosmological N-body simulations in the $\Lambda$CDM cosmology reported in Chapter \ref{chapter3} (first shown in \cite{Ramachandra2015}) shows that at the resolution of the simulation i.e. without additional smoothing, the cosmic web represents a hierarchical structure: each halo is embedded in the filamentary framework of the web predominantly  at the filament crossings, and each filament is embedded in the wall like fabric of the web at the wall crossings.

@@

% number of streams is equal to three or a few.
% \subsection{Multistream view of the dark matter haloes}

\item {\bf Multistream view of the dark matter haloes: } In our simulation reported in Chapter \ref{chapter3}, simple virial density criterion corresponds to a global threshold of $n_{str} \geq 90$ for DM haloes. This shows a reasonably good correspondence with structure finders. A more sophisticated halo finding formulation is done in Chapter \ref{chapter5} assuming that the virialized haloes have convex boundaries. Closed and convex regions of the multistream field are hence isolated by imposing a positivity condition on all three eigenvalues of the Hessian estimated on the smoothed multistream field. In a single-scale analysis of high multistream field resolution and low softening length, the halo substructures with local multistream maxima are isolated as individual halo sites. This halo finding technique is free of any heuristic parameters, and may be extended to delineate filaments, walls, voids, as well as halo sub-structures. Agreement of halo summary statistics (like the halo mass function) of the multistream haloes with traditional halo finders (Friends-of-Friends and Spherical Over-density based techniques) is shown \cite{Ramachandra2017b}. As opposed to several other halo finders, this geometrical approach accounts for non-spherical boundaries, does not find any halo candidates in voids, and minimizes the need for post-processing in the production of halo catalogs for dark matter simulations.

% \subsection{Topological transitions in the cosmic web}

\item {\bf Topological transitions in the cosmic web: } Topological connections in the single-streaming voids and multistreaming filaments and walls reveal a cosmic web structure different from traditional mass density fields, as shown in Chapter \ref{chapter4}. Single streaming voids occupy over 90 per cent of the dark matter Universe. A single void structure not only percolates the multistream field in all the directions, but also spans over 99 per cent of all the single-streaming regions. Sub-grid analyses on scales smaller than simulation resolution reveal tiny pockets of voids that are isolated by membranes of the structure.

@@

\end{itemize}

>>>>

% \begin{itemize}
\subsection{Hierarchical structure of the dark matter web}
Hierarchical structure of the dark matter web: The first study of the multi-stream environment of dark matter haloes in cosmological N-body simulations in the $\Lambda$CDM cosmology reported in Chapter \ref{chapter3} (first shown in \cite{Ramachandra2015}) shows that at the resolution of the simulation i.e. without additional smoothing, the cosmic web represents a hierarchical structure: each halo is embedded in the filamentary framework of the web predominantly  at the filament crossings, and each filament is embedded in the wall like fabric of the web at the wall crossings.

@@

% number of streams is equal to three or a few.
\subsection{Multistream view of the dark matter haloes}

Multistream view of the dark matter haloes: In our simulation reported in Chapter \ref{chapter3}, simple virial density criterion corresponds to a global threshold of $n_{str} \geq 90$ for DM haloes. This shows a reasonably good correspondence with structure finders. A more sophisticated halo finding formulation is done in Chapter \ref{chapter5} assuming that the virialized haloes have convex boundaries. Closed and convex regions of the multistream field are hence isolated by imposing a positivity condition on all three eigenvalues of the Hessian estimated on the smoothed multistream field. In a single-scale analysis of high multistream field resolution and low softening length, the halo substructures with local multistream maxima are isolated as individual halo sites. This halo finding technique is free of any heuristic parameters, and may be extended to delineate filaments, walls, voids, as well as halo sub-structures. Agreement of halo summary statistics (like the halo mass function) of the multistream haloes with traditional halo finders (Friends-of-Friends and Spherical Over-density based techniques) is shown \cite{Ramachandra2017b}. As opposed to several other halo finders, this geometrical approach accounts for non-spherical boundaries, does not find any halo candidates in voids, and minimizes the need for post-processing in the production of halo catalogs for dark matter simulations.

\subsection{Topological transitions in the cosmic web}

Topological transitions in the cosmic web: Topological connections in the single-streaming voids and multistreaming filaments and walls reveal a cosmic web structure different from traditional mass density fields, as shown in Chapter \ref{chapter4}. Single streaming voids occupy over 90 per cent of the dark matter Universe. A single void structure not only percolates the multistream field in all the directions, but also spans over 99 per cent of all the single-streaming regions. Sub-grid analyses on scales smaller than simulation resolution reveal tiny pockets of voids that are isolated by membranes of the structure.

@@

% \end{itemize}
